---
title: "TABLE PREP - all case studies one by one"
subtitle: "...."
author:
- Luisa M. Mimmi^1^ 
- ^1^Economics Advisor at Ministry of Economics & Finance (MEF) - G20
date: "Last updated: `r format(Sys.time(), '%d %B, %Y')`"
output:
  bookdown::word_document2:
    fig_caption: yes
    md_extensions: +footnotes
    reference_docx: ../custom_reference.docx
    toc: no
  bookdown::html_document2:
    toc: yes
    toc_depth: 3
    toc_float: TRUE
    number_sections: no
    code_folding: hide
include.latex: TRUE
---

# Set up + colors
Ho schiarito i colori light x word (ma non cambia )

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)# include R source code in the output 

# Load required packages
if (!require("pacman")) install.packages("pacman")
p_load(here,fs,# dir managmnt
       captioner, # allows you to store figure and table captions and print them later.
       citr, # RStudio Addin to Insert Markdown Citations
       tidyverse, # dplyr,tidyr, ggplot2,readr, purr, stringr, forcats
       magrittr,
       janitor, scales,
       emo, # emojy
       gt,
       readxl,
       ggpubr,
       eulerr , # for venn diagram
       viridis, patchwork, hrbrthemes, fmsb,colormap, # 4 radar chart 
       flextable, #framework for easily create tables for reporting and publications (WORD)
       colortools,
       officer # helper functions for tables 4 flextable in word
       )



# Preparing to make figure and table captions using the captioner package
figs <- captioner(prefix="Figure")
tbls <- captioner(prefix="Table")

#   colori                                                             
	bluMEFprinc	<- "#2D337C"        # "#2D337CFF" (alpha = 1) OR rgb(45/255, 51/255, 124/255, 1)
	 
	gialloMEFprinc <- "#BD8723"       # "#BD8723FF" (alpha = 1) OR rgb(189/255, 135/255, 35/255, 1)
 	gialloMEFlight <- "#BD872333"       # "#BD8723FF" (alpha = 1) OR rgb(189/255, 135/255, 35/255, 0.4)
 
	bluMEFsec	<- "#455A8B"         # "#455A8BFF" (alpha = 1) OR rgb(69/255, 90/255, 139/255, 1)
	bluMEFsec_light	<- "#455A8B33"   
	bordeaux	<- "#854442"       # "#854442FF" (alpha = 1) OR rgb(133/255, 68/255, 66/255, 1)
  bordeaux_light	<- 	"#85444233"
	verde	<- "#285E60"       # "#285E60FF" (alpha = 1) OR rgb(40/255, 94/255, 96/255, 1)
	verde_light	<- "#285E6033"   
	marrone	<-  "#866445"       # "#866445FF" (alpha = 1) OR rgb(134/255, 100/255, 69/255, 1)
		marrone_light	<-  "#86644533" 
	grigio	<-"#A6A6A6"       # "#A6A6A6FF" (alpha = 1) OR rgb(166/255, 166/255, 166/255, 1)
	
	grigioSfondo	<-"#F2F2F2"       # "#F2F2F2FF" (alpha = 1) OR rgb(242/255, 242/255, 242/255, 1)
 
	
	# col2rgb( "#854442")
	
	palette_g20 <- c("#455A8B", "#854442", "#285E60", "#866445",  "#A6A6A6" )
	palette_g20_light <- c(rgb(69/255, 90/255, 139/255, 0.4), rgb(133/255, 68/255, 66/255, 0.4), rgb(40/255, 94/255, 96/255, 0.4), 
	                      rgb(134/255, 100/255, 69/255, 0.4),  rgb(166/255, 166/255, 166/255, 0.4) )
 

blue_scale <- 	colortools::sequential(rgb(45/255, 51/255, 124/255, 1),what = "alpha")
blue_comp <- 	colortools::tetradic(rgb(45/255, 51/255, 124/255, 1) )
bordeaux_scale	<- 	colortools::sequential(rgb(133/255, 68/255, 66/255, 1) , what = "alpha" )
bordeaux_comp	<- 	colortools::tetradic(rgb(133/255, 68/255, 66/255, 1)   )

verde_scale	<- 	colortools::sequential(rgb(40/255, 94/255, 96/255, 1) , what = "alpha" )
verde_comp	<- 	colortools::tetradic(rgb(40/255, 94/255, 96/255, 1)  )
marrone_scale	<- 	colortools::sequential(rgb(134/255, 100/255, 69/255, 1), what = "alpha" )
marrone_comp	<- 	colortools::tetradic(rgb(134/255, 100/255, 69/255, 1))

marrone_scale	<- 	colortools::sequential(rgb(134/255, 100/255, 69/255, 1), what = "alpha" )
marrone_comp	<- 	colortools::tetradic(rgb(134/255, 100/255, 69/255, 1))


grigio_scale	<- 	colortools::sequential(rgb(166/255, 166/255, 166/255, 1), what = "alpha" )
# grigio_comp	<- 	colortools::tetradic(rgb(166/255, 166/255, 166/255, 1)))

	# flextable stuff 
	brdr <- fp_border(color = bluMEFprinc, width = 1.5)
	brdr_in <- fp_border(color = "white", width = 1.5)
```

##### ------ (load files ) 
```{r}
# Load necessary file (prepared in "maintenance_paper/03_Maint_G20cases_PREP.Rmd")
load(here::here("maintenance_paper", "casi.Rdata"))
casi$has_resilience  <- casi$`has_resilience (energy efficiency, natural hazard risk et)`
# Source helper (data cleaning and basic analyses) 
# (if you have more .R files, each will source the previous, then the .Rmd sources the last) 

# source("../r_scripts/helper.R")
#rmarkdown::render(here::here("maintenance_paper", "03_Maint_G20cases_PREP.Rmd"))

# create sample 
sample <- sample_n(casi, 5)
```

##### ------ function to fit FT in Table in Word page 
```{r}
    FitFlextableToPage <- function(ft, pgwidth = 7){
          ft_out <- ft %>% autofit()
          ft_out <- width(ft_out, width = dim(ft_out)$widths*pgwidth /(flextable_dim(ft_out)$widths))
          return(ft_out)
    }
   


```


# (TABLE CASES AT A GLANCE) - just for exe 

Prepare a Table that shows the BASIC (flag, id name, policy, sector)

```{r eval=FALSE, include=FALSE}
sample_glance <- sample %>% 
  dplyr::select(country, flag, name, policy, sector) %>% 
  dplyr::arrange(country) #%>%   filter(country != "FFF (from EU)"	)


class(sample_glance)
 
# Turn to ft and add format 
ft_glance_s <- sample_glance %>%  
  flextable()  %>% 
  compose( j = "flag",
           value = as_paragraph(
             as_chunk(""), 
             as_image(src = flag, width = 0.3, height = 0.2),
             as_chunk("")
           ))  %>% 
  autofit() %>% 
  bold( bold = TRUE, j = "name", part = "body") %>% 
  bold( bold = TRUE,   part = "header") %>% 
  color( color = "white",   part = "header") %>% 
  bg( bg = bluMEFprinc,   part = "header") %>% 
  bg( bg = grigioSfondo, part = "body", source = j) %>% 
  border_outer(border = brdr) %>% 
  border_inner(border = brdr_in)

# --- see output in viewer 
ft_glance_s
save_as_image(x = ft_glance_s, path =  here::here("images", "0_ft_glance_s.png")) # OK!

# ---  save it in Word picture 
# change to prepare with custom function 
  ft_glance_s_w <- FitFlextableToPage(ft_glance_s)

# save in format 
save_as_docx(x = ft_glance_s_w, path =  here::here("images", "0_ft_glance_s_w.docx"))  

# dim_pretty(ft_glance_s)
```



# TABLE for loop no flag (long) 

https://epirhandbook.com/tables-for-presentation.html
https://ardata-fr.github.io/flextable-gallery/gallery/2021-03-26-tennis-players/
https://ardata-fr.github.io/flextable-book/rendering.html#simple-export

## a) (SAMPLE)  
```{r eval=FALSE, include=FALSE, results='asis'}
sampleN <- sample %>% 
  dplyr::rename(
     #newname = old name
  "Name"  = "name", 
  "Country"  = "country", 
  "Sector/s"  = "sector",	
  "Sub-sector/s"  = "sub_sectors",	
  "Administrative level"  = "admin",
  "Key agencies in charge"  = "key_stakes",	#"key_stakes_types",	
  "Policy macro area/s"  = "policy",	
  "Policy specific tool/s"  = "sub_policy_clean",	
    # "launched",
    #	"desc_objective"	,"name"	,
  "Highlights"  = "purpose", 	
  "Intended/achieved outcome/s"  = "intended_outcomes",	
  "Status & timeline"  = "status",	
    # "has_regulatory_innovation",	"has_plan_guidelines_std",	"has_O&M_costs_reduction",	
    # "has_priv",	"has_data_collec",	"has_tech40",	"has_resilience", 
    # "has_knowshar",	"has_age",
  "Additional References"  = "link"
    
  )

                                          


for (i in 1:nrow(sampleN)){
  onecase <- sampleN[i,c("Name", 
                         "Country",  # "id", 
                         # "flag", 
                      "Sector/s",
                      "Sub-sector/s",	
                      "Administrative level", 
                      "Key agencies in charge",	#"key_stakes_types",	
                      "Policy macro area/s",	
                      "Policy specific tool/s",	
                      "Highlights" , 	
                      "Intended/achieved outcome/s",	
                      "Status & timeline",	
                       "Additional References")]
      # attempt header with case name (NON VIENE!) 
      #one_name <- onecase[, 3]
      # print(one_name)}
      
      # attempt flag
      #flag <- onecase$flag[i]


      onecase %>% 
        head() %>% 
        t() %>% 
        as.data.frame() %>% 
        tibble::rownames_to_column() %>% 
        flextable %>% 
        set_header_labels ( "rowname" = "Info", "V1" = "Details") %>% 
        bold( bold = TRUE, i = 1, j= 2,  part = "body") %>% 
        bold( bold = TRUE,  j= 1,  part = "body") %>% 
        bold( bold = TRUE,   part = "header") %>% 
        
        color( color = "white",   part = "header") %>% 
        bg( bg = bluMEFprinc,   part = "header") %>% 
        bg( bg = grigioSfondo, part = "body", source = j) %>% 
        bg(bg = gialloMEFlight, i = 1 , part = "body") %>% 
                bg(bg = verde_light, i = c(9,11) , part = "body") %>% 
                  bg(bg = bordeaux_light, i = 10 , part = "body") %>% 
                # bg(bg = gialloMEFlight, i = 1 , part = "body") %>% 
        border_outer(border = brdr) %>% 
        border_inner(border = brdr_in) %>% 
        # fontsize(  size = 14, part = "header") %>% 
        fontsize(  size = 11, part = "all") %>% 
        
        # compose( i = 3, j= 2, value = as_paragraph(
        #   as_chunk(""),
        #   as_image(src = onecase$flag[i], width = 0.3, height = 0.2),
        #   as_chunk("")
        # )) %>% 
        width(j = 1, 3 ) %>% 
        width(j = 2, 10 ) %>%
        autofit()  -> onecase_ft 
      
  # --- 1) see output in viewer 
  onecase_ft
  
  # PRINT (useful when you want to generate flextable in a loop?  / results='asis'
  flextable_to_rmd(onecase_ft)  # --- html output 
 
  # rmarkdown::word_document() # ---- WORD OUTPUT 
  # print (onecase_ft, preview = "docx") # ---- WORD OUTPUT 2 (no format )
  # print(x = ft, target = here::here( "image", "example_table_powerpoint.docx")) #---- WORD OUTPUT 3 (no format )

# ---  2) save each in Word picture 
# change to prepare with custom function 
onecase_ft_w <- FitFlextableToPage(onecase_ft)

# save in format WORD individually 
dir <-   here::here("images/word/")

# sect_properties <- prop_section(colwidths = c(1,7)#,
#                               # page_size = page_size(orient = "portrait",
#                               #                       width = 8.3, height = 11.7),
#                               # type = "continuous",
#                               # page_margins = page_mar()
#                               )

 
save_as_docx(x = onecase_ft_w, path =  paste0(dir, "case", i,".docx") 
             #,pr_section = sect_properties
             )  

}
```

## ------ combine all word case in 1 single word 
```{r eval=FALSE, include=FALSE}
#docfiles <- list.files(path = dir, pattern = '\\.docx$') 
docfiles <- list.files(path = here::here("images", "word"), pattern=glob2rx("^cas*.docx$"),full.names = TRUE) 
 docfiles
 docfiles[1]

 out_dir <- here::here("images", "word")
 target_w <- paste0(out_dir, "/", "allcase.docx")
 
 
 # Combine all docx
my_doc_all <- read_docx() %>% 
  body_add_docx(src = docfiles[1]) %>%
  body_add_docx(src = docfiles[2]) %>%
  body_add_docx(src = docfiles[3]) %>% 
    body_add_docx(src = docfiles[4]) %>%
  body_add_docx(src = docfiles[5])
 
 
 
# Print combined docx to computer
print(my_doc_all, target = target_w)
```

## b) FOR REALZ 

ALL THE SINGLE TABLES ;) 
```{r  results='asis'}
casiN <- casi %>% 
  dplyr::rename(
    #newname = old name
    "Name"  = "name", 
    "Country"  = "country", 
    "Sector/s"  = "sector",	
    "Sub-sector/s"  = "sub_sectors",	
    "Adminstrative level"  = "admin",
    "Key agencies in charge"  = "key_stakes",	#"key_stakes_types",	
    "Policy macro area/s"  = "policy",	
    "Policy specific tool/s"  = "sub_policy_clean",	
    # "launched",
    #	"desc_objective"	,"name"	,
    "Highlights"  = "purpose", 	
    "Intended/achieved outcome/s"  = "intended_outcomes",	
    "Status & timeline"  = "status",	
    # "has_regulatory_innovation",	"has_plan_guidelines_std",	"has_O&M_costs_reduction",	
    # "has_priv",	"has_data_collec",	"has_tech40",	"has_resilience", 
    # "has_knowshar",	"has_age",
    "Additional References"  = "link"
    )

                                        
# FOR LOOP TO MAKE 1 TABLE FOR EACH OBS 
for (i in 1:nrow(casiN)){
  onecase <- casiN[i,c(#"Name", 
                        "Country",  # "id", 
                       # "flag", 
                       "Sector/s",
                       "Sub-sector/s",	
                       "Adminstrative level", 
                       "Key agencies in charge",	#"key_stakes_types",	
                       "Policy macro area/s",	
                       "Policy specific tool/s",	
                       "Highlights" , 	
                       "Intended/achieved outcome/s",	
                       "Status & timeline",	
                       "Additional References")]
  # attempt header with case name (NON VIENE!) 
  #one_name <- onecase[, 3]
  # print(one_name)}
  
  # attempt flag
  #flag <- onecase$flag[i]

   onecase_ft <- onecase %>% 
        head() %>% 
        t() %>% 
        as.data.frame() %>% 
        tibble::rownames_to_column() %>% 
        flextable %>% 
  # GIVE TITLE 1
        set_header_labels ( "rowname" = "Info", "V1" = "Details") %>%
        bold( bold = TRUE, i = 1, j= 2,  part = "body") %>%
        bold( bold = TRUE,   part = "header") %>%
        color( color = "white",   part = "header") %>%
        bg( bg = bluMEFprinc,   part = "header") %>%
  # GIVE TITLE   2
     set_caption(caption =  paste0(casiN[i,c("Country")], " - ", casiN[i,c("Name")]),# add title
                 autonum = NULL, ) %>%  
        fontsize( i = 1, size = 12, part = "header") %>% 
        bold( bold = TRUE, i = 1,   part = "header")  %>% 

        bold( bold = TRUE,  j= 1,  part = "body") %>% 
        bg( bg = grigioSfondo, part = "body", source = j) %>% 
       # bg(bg = gialloMEFlight, i = 1 , part = "body") %>% 
                bg(bg = verde_light, i = c(8,10) , part = "body") %>% 
                  bg(bg = bordeaux_light, i = 9 , part = "body") %>% 
                # bg(bg = gialloMEFlight, i = 1 , part = "body") %>% 
        border_outer(border = brdr) %>% 
        border_inner(border = brdr_in) %>% 
        # fontsize(  size = 14, part = "header") %>% 
        fontsize(  size = 11, part = "all") %>% 
#FLAG        
        # compose( i = 3, j= 2, value = as_paragraph(
        #   as_chunk(""),
        #   as_image(src = onecase$flag[i], width = 0.3, height = 0.2),
        #   as_chunk("")
        # )) %>% 
     
# LAYOUT      
        # width(j = 1, 3 ) %>% 
        # width(j = 2, 10 ) %>% 
     # autofit() %>%  NOT WITH WORDS  !!!!!!!!! 
  fontsize(  size = 10, part = "body") %>% 
  line_spacing(space =1, part = "body") %>% 
  set_table_properties(width =1, layout = "autofit")    # OK FOR WORD !!!!!!!!!!!!!1111 
   # --- 1) see output in viewer 
  onecase_ft
  
  # PRINT (useful when you want to generate flextable in a loop?  / results='asis'
  #flextable_to_rmd(onecase_ft)  # --- html output 
 
  # rmarkdown::word_document() # ---- WORD OUTPUT 
  # print (onecase_ft, preview = "docx") # ---- WORD OUTPUT 2 (no format )
  # print(x = ft, target = here::here( "image", "example_table_powerpoint.docx")) #---- WORD OUTPUT 3 (no format )

# ---  2) save each in Word picture 
# change to prepare with custom function 
# onecase_ft_w <- FitFlextableToPage(onecase_ft)

# save in format WORD individually 
dir <-   here::here("images/word/")

# sect_properties <- prop_section(colwidths = c(1,7)#,
#                               # page_size = page_size(orient = "portrait",
#                               #                       width = 8.3, height = 11.7),
#                               # type = "continuous",
#                               # page_margins = page_mar()
#                               )

 
save_as_docx(x = onecase_ft, path =  paste0(dir, "case", i,".docx") 
             #,pr_section = sect_properties
             )  

} # END LOOP
```

## ------ combine all word case in 1 single word 
```{r}
#docfiles <- list.files(path = dir, pattern = '\\.docx$') 
docfiles <- list.files(path = here::here("images", "word"), pattern=glob2rx("^cas*.docx$"),full.names = TRUE) 
 docfiles
 docfiles[1]

 out_dir <- here::here("images", "word")
 target_w <- paste0(out_dir, "/", "allcase.docx")
 
 
 # Combine all docx
my_doc_all <- read_docx() %>% 
  body_add_docx(src = docfiles[1]) %>%
  body_add_docx(src = docfiles[2]) %>%
  body_add_docx(src = docfiles[3]) %>% 
    body_add_docx(src = docfiles[4]) %>%
  body_add_docx(src = docfiles[5]) %>% 

  body_add_docx(src = docfiles[6]) %>%
  body_add_docx(src = docfiles[7]) %>%
  body_add_docx(src = docfiles[8]) %>% 
    body_add_docx(src = docfiles[9]) %>%
  body_add_docx(src = docfiles[10])%>%
  
   body_add_docx(src = docfiles[11]) %>%
  body_add_docx(src = docfiles[12]) %>%
  body_add_docx(src = docfiles[13]) %>% 
    body_add_docx(src = docfiles[14]) %>%
  body_add_docx(src = docfiles[15])%>%
   
    body_add_docx(src = docfiles[16]) %>%
  body_add_docx(src = docfiles[17]) %>%
  body_add_docx(src = docfiles[18]) %>% 
    body_add_docx(src = docfiles[19]) %>%
  body_add_docx(src = docfiles[20])%>%
    
     body_add_docx(src = docfiles[21]) %>%
  body_add_docx(src = docfiles[22]) %>%
  body_add_docx(src = docfiles[23]) %>% 
    body_add_docx(src = docfiles[24]) %>%
  body_add_docx(src = docfiles[25])%>%
     
      body_add_docx(src = docfiles[26]) %>%
  body_add_docx(src = docfiles[27]) %>%
  body_add_docx(src = docfiles[28]) %>% 
    body_add_docx(src = docfiles[29]) %>%
  body_add_docx(src = docfiles[30])%>%
      
       body_add_docx(src = docfiles[31]) %>%
  body_add_docx(src = docfiles[32]) %>%
  body_add_docx(src = docfiles[33]) %>% 
    body_add_docx(src = docfiles[34]) %>%
  body_add_docx(src = docfiles[35])%>%
       
        body_add_docx(src = docfiles[36]) %>%
  body_add_docx(src = docfiles[37]) %>%
  body_add_docx(src = docfiles[38]) %>% 
    body_add_docx(src = docfiles[39]) %>%
  body_add_docx(src = docfiles[40])%>%
        
         body_add_docx(src = docfiles[41]) %>%
  body_add_docx(src = docfiles[42]) %>%
  body_add_docx(src = docfiles[43]) 

 
 
# Print combined docx to computer
print(my_doc_all, target = target_w)
```




# NOPE! - TABLE for loop yes flag (wide) 
Error in (function (img_raster, width, height)  : 
  this format is not implemented
```{r eval=FALSE, include=FALSE, results='asis'}
for (i in 1:nrow(sample)){
  onecase <- sample[i,c("id","country", "name",  "flag",
                      "sector",	"sub_sectors",	"admin",
                      "key_stakes",	#"key_stakes_types",	
                      "policy",	"sub_policy_clean",	
                      "launched",
                      #	"desc_objective"	,"name"	,
                      "purpose", 	"intended_outcomes",	"status",	
                      # "has_regulatory_innovation",	"has_plan_guidelines_std",	"has_O&M_costs_reduction",	
                      # "has_priv",	"has_data_collec",	"has_tech40",	"has_resilience", 
                      # "has_knowshar",	"has_age",
                      "link")]
  
  onecase %>% 
    head() %>% 
     t() %>% 
    as.data.frame() %>% 
    tibble::rownames_to_column() %>% 
    flextable %>% 
    compose( j = 2, # BOH 
              i = 4, # BOH 
            value = as_paragraph(
              as_chunk(" "), 
              as_image(src = flag, width = 0.5, height = 0.33)) 
            
    ) %>% 
    autofit()  -> ft 
  
   flextable_to_rmd(ft)  # --- html output 
  
  # rmarkdown::word_document() # ---- WORD OUTPUT 
  # print (ft, preview = "docx") # ---- WORD OUTPUT 2 (no format )
  # print(x = ft, target = here::here( "image", "example_table_powerpoint.docx")) #---- WORD OUTPUT 3 (no format )
}
```



